Learning Discrete-valued Bayesian Network from Mixed Data

### 2015-10-25 BN_discretizer_paper.tex
initialize
update

The rest of the paper is organized as follows: we prepare the preliminaries and notations of Bayesian network in Section 2. Related work, including MDL principle discretization \citep{Friedman_1996} and MODL discretization by \citet{Boulle_2006}, are summarized in Section 3. In Section 4, we introduce the new discretization method, including formulation of objective function and algorithms. One continuous variable case and multiple continuous variable case are also included in this section. Finally, in Section 5, we apply the new discretization method to real-world data and show the result.
%
%\section{Related Work}
%\label{relat_work}
%
%\section{Notation and Preliminaries}
%\label{notat_pre}
%\subsection{Bayesian Network}
%\label{BN}
%A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variable $X = \{  X_1, X_2, \cdots, X_n \}$, and whose edges $E$ represents probabilistic dependencies among nodes. The graph structure $G$ encodes the Markov property: each node $X_i$ is independent of its non-descendants given its parents in $G$. The second component of $B$, namely $\Theta$, contains a set of parameter that qualifies the network. Elements of $\Theta$ take the form $\theta_{x_i|\Pi_{x_i}} = P(x_i|\Pi_{x_i})$ for each possible value $x_i$ of $X_i$, and $\Pi_{x_i}$ of $\Pi_{X_i}$ (the set of parents of $X_i$ in $G$). Due to Markov property, we can represent the multivariate joint distribution over $X$ as
%\begin{equation*}
%P_B (X_1 , \cdots, X_n) = \prod_{i=1}^{n} P_B (X_i | \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i|\Pi_{x_i}}
%\end{equation*}\\
%For a Bayesian network, we can generate its data instances by forward sampling, i.e., sampling variables one by one in a topological order. A topological order is obtained by breadth-first search. Given a instance of $X_i$'s parent set $\Pi_{X_i}$, value of $X_i$ can be sampled according to conditional probability relation $P(X_i | \Pi_{X_i})$. Furthermore, this parent-child sampling order can be reversed if we know the marginal probability of child variable $P(X_i)$. By Bayes rule,
%\begin{equation*}
%P(X_i | \Pi_{X_i}) \cdot \prod_{j = 1}^{ Pa( X_i)} P( \{ \Pi_{X_i} \}_j) = P(X_i) \cdot P(\Pi_{X_i} | X_i),
%\end{equation*}
%where $Pa( X_i)$ is the number of parents of $X_i$, we can first sample $X_i$ by $P(X_i)$, then sample the parent varaibles simultaneously by $P(\Pi_{X_i} | X_i)$. That is to say, $X_i$ becomes the starting point for sampling. $X_i$'s descendants are sampled in the same way as forward sampling. $X_i$'s ancestors are sampled in a reverse order.
%\subsection{K2 Structure Learning}
%\label{K2}
%
%\section{Section title}
%\label{sec:1}
%\subsection{Subsection title}
%\label{sec:2}
%as required. Don't forget to give each section
%and subsection a unique label (see Sect.~\ref{sec:1}).
%\paragraph{Paragraph headings} Use paragraph headings as needed.
%\begin{equation}
%a^2+b^2=c^2
%\end{equation}

% For one-column wide figures use
\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:1}       % Give a unique label
\end{figure}
%
% For two-column wide figures use
\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:2}       % Give a unique label
\end{figure*}
%
% For tables use
\begin{table}
% table caption is above the table
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{lll}
\hline\noalign{\smallskip}
first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number \\
number & number & number \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

>>>>

The rest of the paper is organized as follows: we prepare the preliminaries of Bayesian network in Section 2. Related work, including MDL principle discretization \citep{Friedman_1996} and MODL discretization by \citet{Boulle_2006}, are summarized in Section 3. In Section 4, we introduce the new discretization method, including formulation of objective function and algorithms. One continuous variable case and multiple continuous variable case are also included in this section. Finally, in Section 5, we apply the new discretization method to real-world data and show the result.

\section{Preliminaries}
\label{Prelim}
\subsection{Bayesian Network}
\label{BN_basic}
A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variable $X = \{  X_1, X_2, \cdots, X_n \}$, and whose edges $E$ represents probabilistic dependencies among nodes. The graph structure $G$ encodes the Markov property: each node $X_i$ is independent of its non-descendants given its parents in $G$. The second component of $B$, namely $\Theta$, contains a set of parameter that qualifies the network. Elements of $\Theta$ take the form $\theta_{x_i|\Pi_{x_i}} = P(x_i|\Pi_{x_i})$ for each possible value $x_i$ of $X_i$, and $\Pi_{x_i}$ of $\Pi_{X_i}$ (the set of parents of $X_i$ in $G$). Due to Markov property, we can represent the multivariate joint distribution over $X$ as
\begin{equation*}
P_B (X_1 , \cdots, X_n) = \prod_{i=1}^{n} P_B (X_i | \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i|\Pi_{x_i}}
\end{equation*}\\
For a given Bayesian network, we can generate its data instances by forward sampling, i.e., sampling variables one by one in a topological order \citep[see][chap.~22]{algo_2009}. Given a instance of $X_i$'s parent set $\Pi_{X_i}$, value of $X_i$ can be sampled according to the conditional probability table $P(X_i | \Pi_{X_i})$. Furthermore, this parent-child sampling order can be reversed if we know the marginal probability of child variable $P(X_i)$. By Bayes rule,
\begin{equation*}
P(X_i | \Pi_{X_i}) \cdot \prod_{j = 1}^{ Pa( X_i)} P( \{ \Pi_{X_i} \}_j) = P(X_i) \cdot P(\Pi_{X_i} | X_i),
\end{equation*}
where $Pa( X_i)$ is the number of parents of $X_i$, and $\{ \Pi_{X_i} \}_j$ is the $j$th parent of $X_i$. We can first sample $X_i$ by $P(X_i)$, then sample all the parent varaibles simultaneously by $P(\Pi_{X_i} | X_i)$. That is to say, $X_i$ becomes the starting point for sampling.

\subsection{K2 Structure Learning}
\label{intro_K2}
K2 ...

\section{Related Work}
\label{relat_work}
\subsection{MDL Principle Discretization}
\label{MDL}

\subsection{MODL Discretization}
\label{MODL}

\section{Discretize One Continuous Variable}
\label{one-conti}

\subsection{Notations}
\label{Notation}

\subsection{Objective Function}
\label{obj}

\subsection{Algorithm}
\label{algo}

\subsection{Approximation}
\label{approx}

\section{Discretizing Multiple Continuous Variable with Structure Learning}
\label{multiple-conti}

\section{Experiments}
